Haskell in Computational Biology

### 2013-05-29 jfp.tex
omit needless words

Using the code in \figref{viterbi-hov4}, plus the auxiliary functions
shown above, the implementation of Viterbi's algorithm is just
25~lines of code, of which 2~lines are type signatures.
That's four times smaller than our original code.
But~while we've gained something, we've also lost something---it's not
at all obvious that the code in \figref{viterbi-hov4}  implements
Viterbi's equations.

>>>>

Using the code in \figref{viterbi-hov4}, plus the auxiliary functions
shown above, the implementation of Viterbi's algorithm is just
25~lines of code, of which 2~lines are type signatures.
That's four times smaller than our original code.
But~while we've gained something, we've also lost something---it's not
obvious that the code in \figref{viterbi-hov4}  implements
Viterbi's equations.
